\documentclass{letter}
\usepackage{hyperref}
\newcommand{\usd}[1]{\$#1}
\signature{Jef{}frey Finkelstein}
\address{Jef{}frey Finkelstein \\ 107 Glenville Avenue \\ Boston, MA 02134}
\date{\today}
\begin{document}
\begin{letter}{Internal Revenue Service \\ Disclosure Scanning Operation \\ - Stop 93A \\ Post Office Box 621506 \\ Atlanta, GA 30362-3006}
  \opening{Dear Disclosure Officer:}
  This is a request under the Freedom of Information Act.

  As proof of identity, I declare under penalty of perjury of the laws of the United States of America that the foregoing is true and correct.
  Executed on \today.
  I am Jeffrey Finkelstein and I am requesting that a copy of the following documents be provided to me.
  I do not wish to inspect the documents first.

  I request that the ``Modernized e-File (MeF) Application to Application (A2A) Toolkit'', including but not limited to the source code for the Software Development Kit (SDK) and the client (in all languages for which they exist), be provided to me.
  I request that a list of the authors of the computer program be provided to me.
  I request that this information (computer program and authors) be made available for download at a URL publicly accessible on the World Wide Web.

  I request a speedy response due to the following compelling need.
  I am a person primarily engaged in disseminating information and this is a matter of current exigency to the American public.
  As a graduate student in computer science my job is to understand and disseminate the implications of technology in society (including in our government).
  If the ``A2A'' program has security flaws, it affects millions\footnote{\url{http://www.irs.gov/newsroom/article/0,,id=237000,00.html}} of American taxpayers who file their tax returns electronically.
  The security of any computer program created by the United States government must be publicly verifiable and its authors held accountable.
  This is therefore a matter of current exigency to the American public.

  In order to determine my status for the applicability of fees, you should know that I am an \textbf{``Other'' Requester} seeking information for non-commercial or personal use.

  I am willing to pay fees for this request up to a maximum of \usd{2.56}.
  If you estimate that the fees wil exceed this limit, please inform me first.

  Thank you for your consideration of this request.

  \closing{Sincerely,}
\end{letter}
\end{document}
